How to compute the fusion product of MV cycles in type A

### 2021-04-26 draft.tex
proof amended

\documentclass[draft]{article}
\usepackage{basic}
\usepackage{emoji}

% \setemojifont{Apple Color Emoji}
% Working title: 
\title{How to compute the fusion product of MV cycles in type A}
\author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
% \date{October 2020}
\date{\today}

@@

These isomorphisms glue together to a projection map
$$
\tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
$$ 
(This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)

@@

\begin{theorem} 
\label{th:OGrl}
There is an isomorphism
$$
    \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu 
$$
given by $ (A,s) \mapsto (g(A)\CC[t]^m, s)$.
\end{theorem}
% \acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
% \jcom{Oops, no I think that we should stick with $ X_{0, \AA}$.}
% TODO: comb the doc at the end for this notation 
\begin{proof}
Since we already have the isomorphism from \Cref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, 
$$ 
    (A,s) \in \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu \,. 
$$
This follows immediately from \Cref{le:Grl1l2}.
\end{proof}
% 
\begin{theorem}
\label{th:OTGrW}
The isomorphism from \Cref{th:OGrl} restricts to an isomorphism
$$ 
    \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \UU^{\mu', \mu''}_{0,\AA} \cong \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} \cap S^{\mu', \mu''}_{0,\AA}\,.
$$
\end{theorem}
% 
%\jcom{I was thinking about the proof of this result.  It is enough to prove that for $ A \in \OO^{\lambda', \lambda''}_s \cap \TT_\mu $, $g(A) \in S^{\mu', \mu''}_s $ if and only if $ A \in T^+$.  It is easy to show that if $ A \in \UU$, then $ g(A) \in S^{\mu', \mu''}_s $.  But the converse is not so obvious.  (I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu', \mu''}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu', \mu''}$ and $\UU$ as attracting sets for a $\CC^\times$ action.  Which do you prefer?}
% 
%\acom{Assuming Theorem 2 we think this follows by application of Roger's lemma. Also, I think my thesis is complete on this point.}
% 
%\jcom{I thought about this and I agree with you now.  I will write this up soon.} 
% 
%\acom{But I am also curious about the attracting set approach.}
% 
\begin{proof}
We could prove this by observing the both sides are the attracting locus of an appropriate $ \CC^\times$ action. However, we will give the following more algebraic proof.

Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu', \mu''}_{0,\AA} $.

On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.

On the other hand, if $ (g(A), s) \in S^{\mu', \mu''}_{0,\AA}$, then we can write 
$$
    g t^\mu r= n t^{\mu'} (t-s)^{\mu''}
$$
for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\Oinf) $. % was CC\xt[]
Note that $ h^{-1}n h \in N(\Kinf)$, 
% ((t^{-1}))
so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_{-,1}(\Oinf), n_2 \in N_-(\CC[t])$.  So then after doing a bit of algebra, we reach
$$
    t^\mu r (t^{-\mu} n_2^{-1} t^\mu) t^{-\mu} = g^{-1} h n_1.
$$
Since $ g, h, n_1 \in G_1(\Oinf)$, the right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.

Moreover, since $ \mu $ is dominant, we know that 
$$
    t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.
$$
% $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
Thus, we deduce that $ g^{-1} h n_1 \in N_1(\Oinf)$ 
% $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''} N_1(\Oinf) $.  
% Given that we know that 
Since $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA}$ as desired.
\end{proof}
% 
\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows). To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.  In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
% 
%\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
% 
%\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$. When we multiply by $t^{-\mu}$, we scale the $i$th column by $t^{-\mu_i}$. So the diagonal entries are $1 + p$ where $p \in t^{-1}\CC[t^{-1}]$ while the off-diagonal entries in column $i$ have highest (in $t$) degree $\min(\mu_i-1, \mu_j-1) - \mu_i < 0$. Hence $g \in G_1(\cO_\infty)$.}

\section{Falling Action} % Resolution
\acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis. Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with. This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
% 
\begin{comment}
\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

@@

The variety $X(\tau)$ defined by
% from $\tau\in YT(\lambda)_\mu$ by 
\[
X(\tau) = \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}
}    
\]
is called a generalized orbital variety.

% 
We need the following result from \cite{dthesis}.
\begin{proposition}
    \label{prop:dth}
    (Part of which is a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison})
    There is an isomorphism 
    $\phi: \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \overline\Gr^\lambda\cap S^\mu_-$ 
    and it is compatible with the bijection $YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ 
    in the sense that the irreducible component $\phi(X(\tau))$ associated to the semistandard Young tableau $\tau$ is an open dense subset of the MV cycle whose Lusztig datum is equal to that of $\tau$. 
\end{proposition}

% Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all 
% % but its first $i$ boxes
% boxes of weight exceeding $i$. 
% % If the tableau contains repeated entries then first means leftmost.
% 
\jcom{I don't think that you should mention this partial inverse here.  I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
\acom{Ok, I moved it.}

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
Now let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
In this part we prove that 
% the ideal of 
$Z'\ast_\AA Z''$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
\acom{Need to introduce LD.}
\begin{proposition}
    Given $b_{Z'},b_{Z''}\in\CC[N]$, let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$. Let $\mu = \mu' + \mu''$. If $s\ne 0$, then 
    \[
    \overline{\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\}} 
    \cong Z'\times Z'' \,. %\mu_1 + \cdots + \mu_i
    % = Z(\tau')\times Z(\tau'')\,. 
    \]
\end{proposition}
% 
\jcom{Do you want the ``blocky'' or ``boxy'' description here?  I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$? I'm not so sure that ``boxy'' will work, since with those $s$ in the matrix, it doesn't preserves all the $ \CC^i$.}

\acom{Fixed.}

\begin{proof}
    Let $A$ be an element of the set on the left hand side, let $a\in\{0,s\}$ and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
    % Let $i\in \{1,\dots,N\}$ and write $m(i)$ for the maximum weight of a box in $\tau'(i)$ or $\tau''(i)$.

    The the Jordan type of $(A-a)\big|_{E_a\cap\CC^{|\mu(i)|}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
    Moreover, the lattice $L$ defined by $g(A)$ is such that $t-a$ has the same Jordan type on 
    % $\cO_a^{m(i)} / L(a)\cap\cO_a^{m(i)} = \CC[t]^{m(i)}/L\cap\CC[t]^{m(i)}\otimes_{\CC[t]}\cO_a $ 
    \begin{equation}
        \label{eq:bcflat}
        \cO_a^{|\mu(i)|} / L(a)\cap\cO_a^{|\mu(i)|} = \left(\CC[t]^{|\mu(i)|}/L\cap\CC[t]^{|\mu(i)|}\right)\otimes_{\CC[t]}\cO_a 
    \end{equation}
    as does $(A-a)\big|_{E_a\cap\CC^{|\mu(i)|}}$. 
    % \acom{Not sure when to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
    % 
    % \Cref{eq:bcflat} follows from e.g.\ \cite[Proposition~10.14]{atiyah2018introduction}:
    % \begin{quotation}
    %     If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
    % \end{quotation}
    % applied to $A = \CC[t]$ and $\fa = (t)$. 
    \Cref{eq:bcflat} follows from the fact that a module over a PID is flat if and only if it is torsion free, and $\cO_a$ is clearly torsion free.

@@

    The second assertion is a consequence of \Cref{le:linalg}.
    By \Cref{prop:dth}, it follows that $(L(0),L(s)) \in Z'\times Z''$. 
    Since all maps are isomorphisms the converse is automatic. 
\end{proof}

>>>>

\documentclass[draft]{article}
\usepackage{basic}
\usepackage{emoji}
% TODO: The matrix is lower triangular and the lower-triangular matrix is
% \setemojifont{Apple Color Emoji}
% Working title: 
\title{How to compute the fusion product of MV cycles in type A}
\author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
% \date{October 2020}
\date{\today}

@@

These isomorphisms glue together to a projection map
\begin{equation}
\label{eq:mvitau}
    \tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
\end{equation}
(This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)

@@

\begin{theorem} 
\label{th:OGrl}
There is an isomorphism
$$
    \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu 
$$
given by $ (A,s) \mapsto (g(A)\CC[t]^m, s)$.
\end{theorem}
% \acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
% \jcom{Oops, no I think that we should stick with $ X_{0, \AA}$.}
% TODO: comb the doc at the end for this notation 
\begin{proof}
Since we already have the isomorphism from \Cref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, 
$$ 
    (A,s) \in \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu \,. 
$$
This follows immediately from \Cref{le:Grl1l2}.
\end{proof}
% 
\begin{theorem}
\label{th:OTGrW}
The isomorphism from \Cref{th:OGrl} \acom{should ``Theorem'' etc.\ be capitalized when it appears in the middle of a sentence?}
restricts to an isomorphism
$$ 
    \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \UU^{\mu', \mu''}_{0,\AA} \cong \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} \cap S^{\mu', \mu''}_{0,\AA}\,.
$$
\end{theorem}
% 
%\jcom{I was thinking about the proof of this result.  It is enough to prove that for $ A \in \OO^{\lambda', \lambda''}_s \cap \TT_\mu $, $g(A) \in S^{\mu', \mu''}_s $ if and only if $ A \in T^+$.  It is easy to show that if $ A \in \UU$, then $ g(A) \in S^{\mu', \mu''}_s $.  But the converse is not so obvious.  (I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu', \mu''}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu', \mu''}$ and $\UU$ as attracting sets for a $\CC^\times$ action.  Which do you prefer?}
% 
%\acom{Assuming Theorem 2 we think this follows by application of Roger's lemma. Also, I think my thesis is complete on this point.}
% 
%\jcom{I thought about this and I agree with you now.  I will write this up soon.} 
% 
%\acom{But I am also curious about the attracting set approach.}
% 
\begin{proof}
We could prove this by observing the both sides are the attracting locus of an appropriate $ \CC^\times$ action. However, we will give the following more algebraic proof.

Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu', \mu''}_{0,\AA} $. \acom{not $g(A)\CC[t]^m$}

On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$. \acom{not $g(A)\CC[t]^m$}

On the other hand, if $ (g(A), s) \in S^{\mu', \mu''}_{0,\AA}$, \acom{not $g(A)\CC[t]^m$} then we can write 
$$
    g t^\mu r= n t^{\mu'} (t-s)^{\mu''}
$$
for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\Oinf) $. % was CC\xt[]
Note that $ h^{-1}n h \in N(\Kinf)$, 
% ((t^{-1}))
so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_{-,1}(\Oinf), n_2 \in N_-(\CC[t])$.  So then after doing a bit of algebra, we reach
$$
    t^\mu r (t^{-\mu} n_2^{-1} t^\mu) t^{-\mu} = g^{-1} h n_1.
$$
Since $ g, h, n_1 \in G_1(\Oinf)$, the right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.

Moreover, since $ \mu $ is dominant, we know that 
$$
    t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.
$$
% $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
Thus, we deduce that $ g^{-1} h n_1 \in N_1(\Oinf)$ 
% $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''} N_1(\Oinf) $.  
% Given that we know that 
Since $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA}$ as desired.
\end{proof}
% 
\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows). To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.  In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
% 
%\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
% 
%\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$. When we multiply by $t^{-\mu}$, we scale the $i$th column by $t^{-\mu_i}$. So the diagonal entries are $1 + p$ where $p \in t^{-1}\CC[t^{-1}]$ while the off-diagonal entries in column $i$ have highest (in $t$) degree $\min(\mu_i-1, \mu_j-1) - \mu_i < 0$. Hence $g \in G_1(\cO_\infty)$.}
% 
Restricting to the zero fibre we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. \acom{Technically the zero fibre is comprised of $\CC[t]$ lattices and we need to `specialize' to end up in the ordinary $\Gr$.}
% 
\begin{corollary}
    \label{cor:mvy}
    $\OO^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
\end{corollary}
\section{Falling Action} % Resolution
\acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis. Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with. This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
% 
\begin{comment}
\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

@@

The variety $X(\tau)$ defined by
% from $\tau\in YT(\lambda)_\mu$ by 
\[
X(\tau) = \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}
}    
\]
is called a \textbf{generalized orbital variety}. 
% 
It inherits a crystal datum called a \textbf{Lusztig datum} from its tableau. 
\acom{Cite Joel? Hide dependence on reduced expression?}
The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is got from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
$$
n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
$$
for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
% 
For example, if 
\[
    \tau = \young(1112,23) 
\]
then
\begin{gather*}
%    \text{if } \tau = \young(1112,23) \text{ then } 
\gt(\tau) = \begin{matrix}
       3 \\
       4 & 1 \\ 
       4 & 2 & 0 
   \end{matrix} \text{ and }
   n_\bullet(\tau) = (1,0,1)\,. 
\end{gather*}
% 
% TODO
% \begin{theorem}(CITE KAM07)
%     Taking $\vi$-Luszig datum is a bijection $P\to\NN^{\ell}$. 
% \end{theorem}
% 
We need the following two results from \cite{dthesis}.
\begin{proposition}
    \label{pr:govsasirrecs}
    The decomposition
    \begin{equation*}
        % \label{eq:govsasirrecs}
        \overline{\OO}^\lambda\cap\TT_\mu\cap\n = \bigsqcup_{\tau\in YT(\lambda)_\mu} X(\tau)
    \end{equation*}
    is\dots
\end{proposition}
% 
Denote by $Z(\tau)\subset\Gr$ the image of $X(\tau)$ under the isomorphism of \Cref{cor:mvy}. 
\acom{Still need Lusztig data of MV cycles; with it $B(\infty)$, stable vs ordinary, etc?}
% 
\begin{proposition}
    \label{prop:dth}
    % The isomorphism 
    % $\phi: \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \overline\Gr^\lambda\cap S^\mu_-$ 
    % is compatible with the decomposition of \Cref{pr:govsasirrecs}
    % the bijection $YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ 
    % in the sense that 
    $Z(\tau)$ is dense in the MV cycle whose Lusztig datum is $n_\bullet(\tau)$. 
\end{proposition}
% Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all 
% % but its first $i$ boxes
% boxes of weight exceeding $i$. 
% % If the tableau contains repeated entries then first means leftmost.
% 
\jcom{I don't think that you should mention this partial inverse here.  I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
\acom{Ok, I moved it.}

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
In this part we prove that the product 
% the ideal of 
% $Z'\ast_\AA Z''$ 
$b_{Z'}b_{Z''}\in\CC[N]$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
% 
To begin, let $\tau',\tau''$ be given and let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
%

\acom{We may want to introduce $\ast_s$ in general. For now we make a definition.} Given $s\in\CC$, let 
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,,
\end{equation*}
% 
and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$. If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$ \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}
\begin{proposition}
    % Given $b_{Z'},b_{Z''}\in\CC[N]$, 
    % Let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ 
    % be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$. 
    % and set $\mu = \mu' + \mu''$. If $s\ne 0$, then 
    The image of $X(\tau')\ast_s X(\tau'')$ under the isomorphism of \Cref{th:OTGrW} is dense in $Z(\tau')\ast_s Z(\tau'')$. 
    % \[
    % \overline{\phi(X(\tau',\tau''))} 
    % = Z'\ast_s Z'' \,. 
    % \]
\end{proposition}
% 
% \jcom{Do you want the ``blocky'' or ``boxy'' description here?  I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$? I'm not so sure that ``boxy'' will work, since with those $s$ in the matrix, it doesn't preserves all the $ \CC^i$.}

% \acom{Fixed.}

\begin{proof}
    % The diagram 
    % \[
    % \begin{tikzcd}
    %     \TT_{\mu(i)} \ar[r] \ar[d] & B \ar[d] \\ 
    %     \TT_{\mu(i-1)} \ar[r] & ?? 
    % \end{tikzcd}
    % \]
    % commutes.
    Let $i = 1,\dots, m$, let $a = 0,s$, and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
    Then 
    \begin{enumerate}
        \item $(g(A)\CC[t]^m\cap\CC[t]^i,s) = g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$
        \item \label{eq:twoingredients} $g((A-a)\big|_{E_a \cap \CC^{|\mu(i)|}},a) = \left(g(A) \CC[t]^m \otimes_{\CC[t]}\cO_a \right)\cap \cO_a^i$
        % g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i \otimes_{\CC[t]} \cO_a $
    \end{enumerate}
    \Cref{eq:twoingredients} follows requries \Cref{le:linalg} and the fact that a module over a PID is flat if and only if it is torsion free. % and $\cO_a$ is clearly torsion free

@@

    % In particular, we see that 
    % \[
    % Z(\tau) = \{L \in \Gr: L\cap\CC[t]^i \in \Gr^{\lambda(i)} \text{ for } i = 1,\dots, m\}\,.     
    % \]
\end{proof}
